Place of death in NRS COVID-19 deaths: data processing for analysis

### 2021-07-29 covid_nrs_place_of_death_data.Rmd
there is an error in the openly available data that ODS pulls from, so I recompute the weekly_deaths_overall object from another source, namely from the sex-disaggregated dataset weekly_deaths_sex;
I've messaged the relevant person at ScotGov but for he time being this fix works

# weekly_deaths_sex_age_file <-
#   curl_download(url = "https://www.nrscotland.gov.uk/files//statistics/covid19/weekly-deaths-by-location-age-sex.xlsx",
#                 destfile = tempfile(),
#                 quiet = FALSE)

@@

>>>>

@@

#### Fixing overall weekly deaths

As of 28 July 2021, the [ScotGov open data website](https://statistics.gov.scot/data/deaths-involving-coronavirus-covid-19) reports the non-covid deaths as if they were all-cause deaths, and this messed up my entire pipeline! Below is a quick fix, where instead of using the open data API, I construct the 'overall' weekly deaths data, `weekly_deaths_overall`, from the NRS-published ad-hoc query data on deaths by sex.

```{r}
## quick fix whilst the open data for overall deaths doesn't work...
# TODO: remove this chunk once no longer needed

weekly_deaths_overall_averages_and_other_bits <-  # keep the nrs-computed past averages from the broken data, as well as other columns needed
  weekly_deaths_overall %>%
  select(-c(deaths_covid_related, deaths_non_covid, deaths_all_causes))
  # select(age, sex, place_of_death, week_number_run_over, deaths_nrs_past_average_all_causes, ref_area, ref_period)

weekly_deaths_overall <-  # this rewrites weekly_deaths_overall!
  weekly_deaths_sex %>%
  group_by_all() %>%
  ungroup(sex, starts_with("deaths_")) %>%
  summarise(across(starts_with("deaths_"), .fns = sum), .groups = "drop") %>%  # adds together figures between F & M
  ({function (x) bind_rows(  # this takes the data at this point and a copy of it, and then summarises the copy across place of death, creating an 'All' category, the figures for which are sums across place of death
    x,
    x %>% group_by_all() %>% ungroup(place_of_death, starts_with("deaths_")) %>% summarise(across(starts_with("deaths_"), .fns = sum), .groups = "drop") %>% mutate(place_of_death = "All")
  )}) %>%
  mutate(sex = "all", age = "all") %>%  # add these so that I don't end up breaking any further analysis
  arrange(week_number_run_over, place_of_death) %>%
  left_join(
    weekly_deaths_overall_averages_and_other_bits,
    by = c("week_number", "week_number_run_over", "year", "date_w_c", "place_of_death", "sex", "age")
    )  # add the average numbers in also so I don't break any further analysis
```
